---
title: "Assignment 9"
author: "Neel Epstein"
date: "2023-01-30"
output:
  prettydoc::html_pretty:
    theme: lumen
---

## Question 1
#### Using a for loop and an if statement, write a function to calculate the number of zeroes in a numeric vector. Before entering the loop, set up a vector of integers with some zero values. Then, set up a counter variable counter <- 0. Inside the loop, add 1 to counter each time you have a zero in the vector. Finally, use return(counter) for the output.

```{r}
set.seed(123)
myVec <- sample(-100:100, 10000, replace=TRUE)
zero_counter <- function(x = NULL) {
  counter <- 0
  for (i in 1:length(x)) {
    if (x[i] == 0) {
      counter <- counter + 1
    }
  }
  return(counter)
}
zero_counter(myVec)
```

## Question 2
#### Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number.

```{r}
integers <- sample(0:10, 2, replace = TRUE)
  
  matrix_maker <- function(x = NULL) {
  m <- matrix(nrow=integers[1],ncol=integers[2],byrow=TRUE)
  for(i in 1:integers[1]){
  for(j in 1:integers[2]){
    m[i,j] <- i * j
  }
  }
  return(m)
}
matrix_maker(integers)
```


##Question 3
#### Use a for loop to repeat your previous functions from Weekly Assignment 2 (which simulate a data frame and extract a p-value) 100 times. Store the results in a data frame that has 1 column indicating the replicate number and 1 column for the p-values (a total of 2 columns and 100 rows).

```{r}
set.seed(123)
df_function <- function() {
  df <- data.frame(Type = c(rep("Control", 25),
                      rep("Treatment", 25)), 
            Value = c(rnorm(25, 10, 1.5),
                      rnorm(25, 45, 2)))
  return(df)
}

p_value <- function(df) {
  anova <- aov(data = df, df[,2] ~ df[,1])
  pVal <- summary(anova)[[1]][["Pr(>F)"]][1]
  return(pVal)
}

p_value_results <- data.frame(replicate = integer(length = 100), pvalue = numeric(length = 100))

for (i in 1:100) {
  df <- df_function()
  pVal <- p_value(df)
  p_value_results[i,] <- c(i, pVal)
}
p_value_results
```

